Sky Tomography for 3D Aerosol Distribution Recovery

### 2013-07-26 article.tex
bookmark

Consider a set of ground-based wide-angle cameras
 %~\cite{Cossairt2011, Peleg01omnistereo:panoramic, Koppal:2011:WMS:2191740.2192152}
looking upwards (\cref{fig:groundgrid}). The set performs {\em integral imaging}~\cite{integral} of the sky. Per viewpoint, the view azimuth and elevation angles (relative to the zenith and north) are
encapsulated in the vector ${\bm{\Theta}}$. Any camera $c$ is at a distinct fixed location ${\bm x}$, capturing raw image $i_c({\bm{\Theta}})$. This paper takes the first step, of formulating
a principle of recovering the 3D atmospheric aerosols distribution, using such data. To show feasibility, we perform radiative transfer using two different forward models, enabling cross-validation.
A forward model takes as input the 3D aerosol distribution, and outputs images as if
captured at various viewpoints. One model uses Monte Carlo (MC) methods (\cref{sec:monte-carlo-simul}): it is stochastic, slow but naturally expresses multiple-scattering. Hence, this approach simulates realistic
scenes of arbitrary complexity.  The second model uses the single-Scattering approximation
(\cref{sec:single-scatt-model}). It is less accurate than MC, but derives an analytic closed
form solution to the radiative transfer. This closed form enables simple inversion of
the model, to estimate the underlying atmosphere (\cref{sec:inverse-problem}).

@@

A camera pixel collects light from a narrow cone in the
atmosphere. The cone includes some voxels, intersects with some other
voxels, and oblivious to all the rest~(\cref{fig:projection}b).
%\begin{figure}
%  \centering
%  \yoavcomment{\def\svgwidth{0.8\columnwidth}\input{images/light_transfer.pdf_tex}}
%  \caption{\small [a] Irradiance of voxel $k$ is attenuated by voxels
%    above it on a SR. The scattered radiance from voxel $k$ is then
%    attenuated by voxels below it on a LOS to camera $c$.  [b] An
%    image pixel captures light emanating in a cone in space. Voxels
%    that fully or partially fall in this cone are sensed by the
%    pixel.}
%  \label{fig:projection}
%\end{figure}
Thus light power captured at a pixel is a weighted sum of the power
$p_c(k)$ from all voxels.  This linear sum is formulated by a matrix
operation over ${\bm p}_c$. The measured image is column-stacked to a
vector $N_{\rm pix}$ long. It is given by
\begin{equation}
  {\bm i}_c= {\vect{\Pi}}_c{\bm p}_c
  \;\;.
  \label{eq:IcP}
\end{equation}

@@

We solve~\cref{eq:minobjectiveA} using standard optimization tools.
The gradient of $F$ with respect to ${\bm n}$ is
\begin{align}
  \Grad{{\bm n}} F = -2\sum_{c=1}^{N_{\rm views}}
  \transpose{\left[{\bm J}_{{\bm i}_c}({\bm n})\right]} [{\bm i}^{\rm
    measured}_c - {\bm i}_c({\bm n})] + 2 \cdot \eta \cdot
  \Laplacian^T\Laplacian{\bm n} \;.
  \label{eq:gradient1}
\end{align}
Here the matrix ${\bm J}_{{\bm i}_c}({\bm n})$ is the Jacobian of the
vector ${\bm i}_c$ with respect to ${\bm n}$. A close-form expression of
our Jacobian is
\begin{align}
  {\bm J}_{{\bm i}_c}({\bm n}) &= L^{\rm TOA}({\bm A}-{\bm B}){\bm C}
  ,
  \label{eq:gradient2}
\end{align}
where
\begin{align}
  \label{eq:gradient3}
  {\bm A} &= \varpi^{\rm aerosol}\sigma^{\rm aerosol}
  \OpDiag{ P_g^{\rm aerosol}(\vect{\Phi}^{\rm scatter}_c)} \nonumber\\
  {\bm B} &= {\sigma}^{\rm aerosol}\transpose{{\bm D}_c} \nonumber\\
  & \;\;\; \OpDiag{[\tilde{\vect{\alpha}}^{\rm air}_c + \varpi^{\rm
      aerosol}\sigma^{\rm aerosol} P^{\rm aerosol}_g(\vect{\Phi}^{\rm
      scatter}_c) \odot{\bm n}
    ]} \nonumber \\
  {\bm C} &= \OpDiag{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm
      aerosol} {\bm D}_c {\bm n})]} \transpose{{\vect{\Pi}}_c}
\end{align}
For a detailed derivation of \cref{eq:gradient2,eq:gradient3}, we
refer the reader to \cref{sec:gradient-derivation}.

@@

Here we detail the derivation of the gradient of the objective
function:
\begin{equation}
  \label{eq:objectiveA}
  F({\bm n})
  = \sum_{c=1}^{N_{\rm views}}
  \| {\bm i}^{\rm measured}_c - {\bm i}_c({\bm n})\|^2_2
\end{equation}
Here ${\bm i}^{\rm measured}_c$ is the image captured by camera $c$
and ${\bm i}_c({\bm n})$ is an image modeled from the viewpoint of
camera $c$ according to the density distribution ${\bm n}$. In
\cref{sec:captured-image} article we show that ${\bm i}_c({\bm n})$
can be expressed by
\begin{align}
  {\bm i}_c= L^{\rm TOA} {\vect{\Pi}}_c \Big\{ e^{-(\vect{\tau}_c^{\rm
      air} + {\sigma}^{\rm aerosol} {\bm D}_c {\bm n}) }\odot
  \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;
  \nonumber \\
  [\tilde{\vect{\alpha}}^{\rm air}_c + %\right.
  \varpi^{\rm aerosol}\sigma^{\rm aerosol} P^{\rm
    aerosol}_g(\vect{\Phi}^{\rm scatter}_c) \odot{\bm n} ] \Big\} .
  \label{eq:bigIA}
\end{align}

The gradient of $F$ with respect to ${\bm n}$ is
\begin{align}
  \Grad{{\bm n}} F = -2\sum_{c=1}^{N_{\rm views}}
  \transpose{\left[{\bm J}_{{\bm i}_c}({\bm n})\right]} [{\bm i}^{\rm
    measured}_c - {\bm i}_c({\bm n})] \;.
  \label{eq:gradient1}
\end{align}
Here the matrix ${\bm J}_{{\bm i}_c}({\bm n})$ is the Jacobian of the
vector ${\bm i}_c$ with respect to ${\bm n}$. Element $(\Theta,k)$ of
this matrix differentiates the intensity in pixel ${\bm \Theta}$ (in
viewpoint $c$) with variation of the density at voxel $k$, i.e.,
$\partial i_c({\bm \Theta})/\partial{n^{\rm aerosol}(k)}$.

In order to describe the derivation of the Jacobian ${\bm J}_{{\bm
    i}_c}({\bm n})$, we first show some results relating to
differentiation. Let $\vect{n}$ be a vector of length $q$. Let
$\vect{g}(\vect{n})$ be a vector function: it outputs a vector of
length $r$. Let $\mat{B}$ be a $q \times r$ matrix and
\begin{align}
  \vect{g}(\vect{n}) = \exp^{-\transpose{\mat{B}}\vect{n}}.
  \label{eq:example1}
\end{align}
In \cref{eq:example1}, the exponential is element-wise (not raising an
operator to some power). Then
\begin{align}
  \label{eq:partial2}
  \PartDeriv{\vect{g}}{\vect{n}} &= - \mat{B} \,
  \OpDiag{\exp^{-\transpose{\mat{B}}\vect{n}}}
\end{align}
Here we denote by $\OpDiag{\vect{v}}$ conversion of vector $\vect{v}$
into a diagonal matrix, whose main diagonal elements correspond to the
elements of $\vect{v}$. Using \cref{eq:partial2} we can calculate
\begin{align}
  \label{eq:partial4}
  \PartDeriv{\exp^{-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm aerosol}
      {\bm D}_c {\bm n})}}
  {\vect{n}} &= - {\sigma}^{\rm aerosol}\transpose{\OpDistance_c} \,
  \OpDiag{\exp^{-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm aerosol}
      {\bm D}_c {\bm n})}}
\end{align}
In \cref{eq:partial4} we assume that $\vect{\tau}_c^{\rm air}$ is
known and constant.

>>>>

Consider a set of ground-based wide-angle cameras
% ~\cite{Cossairt2011, Peleg01omnistereo:panoramic,
% Koppal:2011:WMS:2191740.2192152}
looking upwards (\cref{fig:groundgrid}). The set performs {\em
  integral imaging}~\cite{integral} of the sky. Per viewpoint, the
view azimuth and elevation angles (relative to the zenith and north)
are encapsulated in the vector ${\bm{\Theta}}$. Any camera $c$ is at a
distinct fixed location ${\bm x}$, capturing raw image
$i_c({\bm{\Theta}})$. This paper takes the first step, of formulating
a principle of recovering the 3D atmospheric aerosols distribution,
using such data. To show feasibility, we perform radiative transfer
using two different forward models, enabling cross-validation.  A
forward model takes as input the 3D aerosol distribution, and outputs
images as if captured at various viewpoints. One model uses Monte
Carlo (MC) methods (\cref{sec:monte-carlo-simul}): it is stochastic,
slow but naturally expresses multiple-scattering. Hence, this approach
simulates realistic scenes of arbitrary complexity.  The second model
uses the single-Scattering approximation
(\cref{sec:single-scatt-model}). It is less accurate than MC, but
derives an analytic closed form solution to the radiative
transfer. This closed form enables simple inversion of the model, to
estimate the underlying atmosphere (\cref{sec:inverse-problem}).

@@

A camera pixel collects light from a narrow cone in the
atmosphere. The cone includes some voxels, intersects with some other
voxels, and oblivious to all the rest~(\cref{fig:projection}b).
% \begin{figure}
%   \centering
%   \yoavcomment{\def\svgwidth{0.8\columnwidth}\input{images/light_transfer.pdf_tex}}
%   \caption{\small [a] Irradiance of voxel $k$ is attenuated by
%   voxels above it on a SR. The scattered radiance from voxel $k$ is
%   then attenuated by voxels below it on a LOS to camera $c$.  [b] An
%   image pixel captures light emanating in a cone in space. Voxels
%   that fully or partially fall in this cone are sensed by the
%   pixel.}
%   \label{fig:projection}
% \end{figure}
Thus light power captured at a pixel is a weighted sum of the power
$p_c(k)$ from all voxels.  This linear sum is formulated by a matrix
operation over ${\bm p}_c$. The measured image is column-stacked to a
vector $N_{\rm pix}$ long. It is given by
\begin{equation}
  {\bm i}_c= {\vect{\Pi}}_c{\bm p}_c
  \;\;.
  \label{eq:IcP}
\end{equation}

@@

We solve~\cref{eq:minobjectiveA} using standard optimization tools.
The gradient of $F$ with respect to ${\bm n}$ is
\begin{align}
  \Grad{{\bm n}} F = -2\sum_{c=1}^{N_{\rm views}}
  \transpose{\left[{\bm J}_{{\bm i}_c}({\bm n})\right]} [{\bm i}^{\rm
    measured}_c - {\bm i}_c({\bm n})] + 2 \cdot \eta \cdot
  \Laplacian^T\Laplacian{\bm n} \;.
  \label{eq:gradient1}
\end{align}
Here the matrix ${\bm J}_{{\bm i}_c}({\bm n})$ is the Jacobian of the
vector ${\bm i}_c$ with respect to ${\bm n}$.  Element $(\Theta,k)$ of
this matrix differentiates the intensity in pixel ${\bm \Theta}$ (in
viewpoint $c$) with variation of the density at voxel $k$, i.e.,
$\partial i_c({\bm \Theta})/\partial{n^{\rm aerosol}(k)}$.  A
close-form expression of our Jacobian and its detailed derivation is
given in \cref{sec:gradient-derivation}.

@@

Here we detail the derivation of the Jacobian ${\bm J}_{{\bm
    i}_c}({\bm n})$ from \cref{eq:gradient1}. First show some results relating to
differentiation. Let $\vect{n}$ be a vector of length $q$. Let
$\vect{g}(\vect{n})$ be a vector function: it outputs a vector of
length $r$. Let $\mat{B}$ be a $q \times r$ matrix and
\begin{align}
  \vect{g}(\vect{n}) = \exp^{-\transpose{\mat{B}}\vect{n}}.
  \label{eq:example1}
\end{align}
In \cref{eq:example1}, the exponential is element-wise (not raising an
operator to some power). Then
\begin{align}
  \label{eq:partial2}
  \PartDeriv{\vect{g}}{\vect{n}} &= - \mat{B} \,
  \OpDiag{\exp^{-\transpose{\mat{B}}\vect{n}}}
\end{align}
Here we denote by $\OpDiag{\vect{v}}$ conversion of vector $\vect{v}$
into a diagonal matrix, whose main diagonal elements correspond to the
elements of $\vect{v}$. Using \cref{eq:partial2} we can calculate
\begin{align}
  \label{eq:partial4}
  \PartDeriv{\exp^{-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm aerosol}
      {\bm D}_c {\bm n})}}
  {\vect{n}} &= - {\sigma}^{\rm aerosol}\transpose{\OpDistance_c} \,
  \OpDiag{\exp^{-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm aerosol}
      {\bm D}_c {\bm n})}}
\end{align}
In \cref{eq:partial4} we assume that $\vect{\tau}_c^{\rm air}$ is
known and constant.
